\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage{cmbright}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[sf]{libertine}
\usepackage{microtype}
\usepackage{multicol}
\usepackage{paracol}
\usepackage{supertabular}
\usepackage{titlesec}
\hypersetup{colorlinks, urlcolor=black, linkcolor=black}

% Geometry
\geometry{hmargin=0.75cm, vmargin=0cm}
\columnratio{0.65, 0.35}
\setlength\columnsep{0.05\textwidth}
\setlength\parindent{0pt}
\setlength{\smallskipamount}{8pt plus 3pt minus 3pt}
\setlength{\medskipamount}{16pt plus 6pt minus 6pt}
\setlength{\bigskipamount}{24pt plus 8pt minus 8pt}

% Style
\pagestyle{empty}
\titleformat{\section}{\scshape\LARGE\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{\bigskipamount}{\smallskipamount}
\newcommand{\heading}[2]{\centering{\sffamily\Huge #1}\\\smallskip{\large{#2}}}
\newcommand{\entry}[4]{{{\textbf{#1}}} \hfill #3 \\ #2 \hfill #4}
\newcommand{\tableentry}[3]{\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]}}

\begin{document}

\vspace*{\fill}

\begin{paracol}{2}

% Name & headline
% \heading{Vadim Zbarashchenko}{Lorem ipsum dolor sit amet, \\ consectetur adipiscing elit.}

\heading{Vadim Zbarashchenko}{Backend Developer}

\bigskip

Enthusiast. Experienced in UNIX systems. Keen on making process automation more efficient. Passionate about developing software that makes lives better worldwide. Have a system view of software development process.

\switchcolumn

% Identity card
\vspace{0.01\textheight}
\begin{supertabular}{ll}
  \footnotesize\faPhone & \href{tel:+79266708867}{+7 926 670 88 67} \\
  \footnotesize\faEnvelope & \href{mailto:john.doe@gmail.com}{vvz.dev@gmail.com} \\
  \footnotesize\faPaperPlane &
  \href{https://t.me/metafates}{t.me/metafates}\\
  \footnotesize\faGithub & \href{https://github.com/metafates}{github.com/metafates} \\
\end{supertabular}

\bigskip
\switchcolumn*

\section{education}

\medskip

\entry{Innopolis University}{Computer Science}{Innopolis, Russia}{2021 -- 2025}

\begin{multicols}{2}
    \begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item[-] Networks
  \item[-] Data Structures \& Algorithms
  \item[-] Databases
  \item[-] Operating Systems
  \item[-] DevOps
    \end{itemize}
\end{multicols}

\switchcolumn

\section{skills}
\begin{supertabular}{rl}
  \tableentry{\footnotesize\faCode}{Go \textperiodcentered{} Rust \textperiodcentered{} Python \textperiodcentered{} Docker}{}
  \tableentry{}{Lua \textperiodcentered{} JavaScript \textperiodcentered{} Nix}{}
  \tableentry{}{Git \textperiodcentered{} Linux \textperiodcentered{} Shell}{}
  \tableentry{}{GitHub Actions \textperiodcentered{} REST \textperiodcentered{} GraphQL}{}
  \tableentry{}{MongoDB}{}
  \tableentry{}{Text Processing \textperiodcentered{} Web Scraping}{}
  \tableentry{}{}{}

  \tableentry{\footnotesize\faSmileBeam[regular]}{Conflict Resolution \textperiodcentered{} Flexibility}{}
  \tableentry{}{Teamwork \textperiodcentered{} Engagement}{}
  \tableentry{}{}{}

  \tableentry{\footnotesize\faLanguage}{English \textperiodcentered{} B2}{}
\end{supertabular}

\switchcolumn

\section{experience}

\entry{Innopolis}{Backend Developer}{Innopolis, 2023}{Python, FastAPI, Docker}

\begin{flushleft}
    \begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
        \item Developed backend server to improve Innopolis University room booking service backed by Microsoft Outlook API.
        \item Outperformed existing system
        \item Implemented additional functionality.
    \end{itemize}
\end{flushleft}

\medskip

\entry{Advanced Web Scraper Project}{Developer}{2022}{Go, Lua, Web Scraping, Image processing, CLI}

\begin{flushleft}
    \begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
        \item Identified the problem with existing open-source solutions and developed web scraping program for comic sites with Lua extension-based architecture.
        \item 700+ stars on GitHub
        \item 10000+ downloads.
    \end{itemize}
\end{flushleft}

\medskip

\entry{Document Converter Project}{Developer}{2022}{Rust, Websockets, CLI}

\begin{flushleft}
    \begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
        \item Investigated the lack of open-source programs for converting Markdown documents into portable HTML pages with embed images and live preview.
        \item Resulting app made process of submitting university assignments more productive.
    \end{itemize}
\end{flushleft} 

\switchcolumn

\section{awards}
\begin{supertabular}{rl}
  \tableentry{2023}{\textbf{Winner}}{}
  \tableentry{}{Open-Source Projects Contest}{spaceafter}
\end{supertabular}

\medskip

\section{other interests}
\begin{supertabular}{rl}
  \tableentry{Tech}{Open Source \textperiodcentered{} Linux}{spaceafter}
  \tableentry{}{Reproducible Systems}{}
  \tableentry{}{}{}
  \tableentry{Sport}{Swimming \textperiodcentered{} Workout}{spaceafter}
  \tableentry{}{}{}
  \tableentry{Other}{Foreign Languages}{}
\end{supertabular}

\medskip

% \section{other projects}

% \begin{flushleft}
%     I am actively engaging with other developers on GitHub. Other projects are available there.
% \end{flushleft}

\end{paracol}

\vspace*{\fill}

\end{document}